Dissecting Neural Style Transfer

### 2019-05-26 paper/paper.tex
1

The style loss $L_\text{content}$ can actually be a sum of several style losses, or sometimes just one.
For each style loss, 
both the current image under optimisation and the style image are passed through the vgg19 model.
The two outputs of a certain function in the model are extracted, 
and converted to Gram matrices. We will elabrate on what Gram matrices are later.
For now a Gram matrix is just a square matrix computed from a multidimensional array (i.e. a feature map).
For example, the Gram matrix (in the style transfer algorithm) of a $1\times64\times512\times512$ array
is a $64\times64$ matrix.
The point is to compute something that describe the distributions of features
in the image without the spatial information of where the features are.
Gram matrices describe the distributions with correlation between features.
The several style losses are computed with the outputs of different functions.
Otherwise, each of the several style losses are computed in exactly the same way.
Again outputs of which functions in the model to derive style losses from is really adjustable.
A nice default is \verb|conv_1|,\verb|conv_2|,...,\verb|conv_5|. We illustrate
the style losses derived from the output of \verb|conv_1| in Figure $\ref{styleloss}$.

>>>>

The style loss $L_\text{content}$ can actually be a sum of several style losses, or sometimes just one.
For each style loss, 
both the current image under optimisation and the style image are passed through the vgg19 model.
The two outputs of a certain function in the model are extracted, 
and converted to Gram matrices. We will elabrate on what Gram matrices are later.
For now a Gram matrix is just a square matrix computed from a multidimensional array (i.e. a feature map).
For example, the Gram matrix (in the style transfer algorithm) of a $1\times64\times512\times512$ array
is a $64\times64$ matrix.
The point is that a Gram matrix describes the distribution of features
in the image without the spatial information of where the features are.
Gram matrices describe the distribution with correlation between features.
The several style losses are computed with the outputs of different functions.
Otherwise, each of the several style losses are computed in exactly the same way.
Again, the outputs of which functions in the model to derive style losses from is really adjustable.
A nice default we used was \verb|conv_1|,\verb|conv_2|,...,\verb|conv_5|. We illustrate
the style losses derived from the output of \verb|conv_1| in Figure $\ref{styleloss}$.
